---
title: "R Notebook"
output: html_notebook
---



Data cleaning 
```{r}
library(tidyverse)
library(DataExplorer)

poverty <- read_csv(file = "Train.csv")
poverty_test <-read_csv(file ="Test.csv")
poverty$tag <-"Train"
poverty_test$tag <-"Test"

poverty_test $Target <-1
poverty_total <- rbind(poverty,poverty_test)
poverty_total <- poverty_total %>% mutate(Target=as.factor(Target))
poverty_total$v2a1 <-NULL  #NA
poverty_total$v18q1 <-NULL  #NA
poverty_total$rez_esc <-NULL #NA   #33413
#names(which(sapply(poverty_total, anyNA)))
poverty_total$meaneduc <-NULL
poverty_total$SQBmeaned <-NULL

poverty_total$dependency <- NULL
poverty_total$idhogar <-NULL






full = as_tibble(rbind(poverty %>% select,poverty_test))

# Create a list of the features names that need to be reverse engineered

feature_list = c(
  "pared",
  "piso",
  "techo",
  "abasta",
  "sanitario",
  "energcocinar",
  "elimbasu",
  "epared",
  "etecho",
  "eviv",
  "estadocivil",
  "parentesco",
  "instlevel",
  "tipovivi",
  "lugar",
  "area"
)

# Matrix to store our new features

new_features_integer = data.frame(matrix(ncol = length(feature_list), nrow = nrow(full)))

# Cycle through and reverse the OHE process for these

ohe_names = vector()

for(i in 1:length(feature_list)){
  
  # Grab the feature
  
  feature_to_fix = full %>% select(starts_with(feature_list[i]))
  
  # Fix and enter into our new feature matrix
  
  new_features_integer[,i] = as.integer(factor(names(feature_to_fix)[max.col(feature_to_fix)], ordered = FALSE))
  names(new_features_integer)[i] = paste0(feature_list[i],"_int")
  
  ohe_names = c(ohe_names, as.vector(names(feature_to_fix)))
  
}

# for(i in 1:length(feature_list)){
#   poverty =poverty %>% select(-starts_with(feature_list[i]))
# }
# poverty_total=as_tibble(cbind(poverty , new_features_integer))

```



Variables Distribution Analysis


We want to see how household variables that discribe different perspectives of household are distributed in our model. Some are normally distirbuted, some are left-skewed, and some do not possess certain patterns. And we use different colors to differenciate different levels of poverty.(with 1 being the extremely poor individuals, with 4 being the non vulnerables)

The variable that represent number of all rooms in the house are normally distributed. <br/>
The variable that represent size of the household and number of mobile phones are left-skewed.<br/>
The variable that represent years of years of schooling do not possess a certain pattern. 

Within each distribution, we can see that the non vulnerables group takes up most percentanges. This is due to the fact that our datasets naturally contains more non vulnerables. 


Later in the Pinciple Component Analysis Section, we will choose 10 prinicipal components that explain the variances most. Thus, we would not bother to transform the data for our multinomial logistics model in our project.


```{r}

a<-ggplot(poverty,aes(x=rooms))+geom_bar(aes(fill=as.factor(Target)))+ylab("Count")+xlab("Number of All Rooms in the House")+labs(fill="Poverty")

b<-ggplot(poverty,aes(x=tamhog))+geom_bar(aes(fill=as.factor(Target)))+ylab("Count")+xlab("Size of the Household")+labs(fill="Poverty")

c<-ggplot(poverty,aes(x=escolari))+geom_bar(aes(fill=as.factor(Target)))+ylab("Count")+xlab("Years of Schooling")+labs(fill="Poverty")

d<-ggplot(poverty,aes(x=qmobilephone))+geom_bar(aes(fill=as.factor(Target)))+ylab("Count")+xlab("Number of Mobile Phones")+labs(fill="Poverty")

grid.arrange(a,b,c,d, nrow = 2,top="Variables Distribution Analysis")


```

PCA

The most important vairable (PC1) and second most important variable(PC2) explain 16.8% of the variances of the dataset in total. 


From the graph, We want to interpret these two variables:


PC1 is largely related with numnber of people in the households and how crowded the home is. 
Some contributing variables are: 
hogar_total, # of total individuals in the household
r4t3, Total persons in the household
hhsize, household size
hogar_nin, Number of children 0 to 19 in household
overcrowding  # persons per room


PC2 is largely related with education: 
Some contributing variables are: 
esolari, years of schooling
SQBescolari, escolari squared

The first 10 principal components chosen by the PCA explain 36.9% of the dataset variances, which is pretty significant in our model. 

....

```{r}
library(ggplot2)
library(RColorBrewer)

poverty_numerical = poverty_total %>% select_if(is.numeric)  ## get the numerical columns 
poverty_numerical$elimbasu5 <- NULL

full_pca = prcomp(poverty_numerical, center = TRUE, scale. = TRUE)

fviz_pca_var(full_pca,
             col.var = "contrib", 
             gradient.cols = c("#FC4E07","#00AFBB","#E7B800"),
             select.var = list(contrib = 30), # top 30 contributing
             repel = TRUE,
             title="PCA-Plot")

library(factoextra)
fviz_eig(full_pca, addlabels=TRUE)

# view <- full_pca$rotation
# to view how to interpret the coefficients 
# might be too many 

```


Some additional data handling 

```{r}


poverty_total= poverty_total %>% 
  cbind(full_pca$x[,1:10])
poverty_train <- subset(poverty_total, tag=="Train")
poverty_test <- subset(poverty_total, tag=="Test")
poverty_test$Target <-NULL

```




split data 
```{r}
seed <-100
set.seed(seed)
inTraining <-createDataPartition(poverty_train$Target,p=0.7,list=FALSE)
poverty_train_training = poverty_train[inTraining,]
poverty_train_validation = poverty_train[-inTraining,]

```



Multinomial

In the dataset we are working on, the dependent variables have 4 different levels, instead of 2. So we use the multinomial logistics regression model.  

[Confusion Matrix Interpretation]

In the validation dataset, the model has a overall accuracy of 0.6482. Out of the predictions of Extreme Poverty,Moderate Porverty, Vulnerable Households and Non Vulnerable Households, we got 64.82% of the predictions correctly. 

For the prediction of Extreme poverty(Class 1), the model has a sensitivity of 2.2%, a Pos Pred Value of 41.67%. This suggsts that

1) Out of individuals who are actually extremely poor, we successfully predict about 2.2% of the times. The model does not perform very well in terms of this metric.

2) Out of all the individuals that we predict to be extremely poor, 41.6% are actually extreme poor. 


[Coefficient analysis]

With PC1, it has a negative relationship with the poverty level. The coefficient PC1 of multinomial logistics is negative, suggesting that with PC1, individuals are more likely to be turning to the poorer level. Remember that in the EDA section, we discovered that PC1 is related with overcrowding of the household. That suggests that if household is more crowded, than the household is more likely on average to be poorer.

The coefficient PC2 of multinomial logistics regression is positive, suggesting that with PC2, individuals are more likely to be turning to the non vulnerable level. And again in the EDA section, we discovered that PC2 is related with years of schooling. That suggests that with more years of schooling, the household is more likely on average to be richer. 

All of the 2 coefficient analysis makes sense intuitively: When households are poorer, their homes are more likely to be crowded and they have more people in a home. When households are richer, they have longer years of schooling because they are able to afford the huge amount of tuitions and living costs. 

Again when we look back to the EDA: we are able to find similar patterns. 


```{r}

library(nnet)
library(caret)

poverty_multinolog <- multinom(Target ~PC1+PC2+PC3+PC4+PC5+PC6+PC7+PC8+PC9+PC10, data=poverty_train_training)
summary(poverty_multinolog)

poverty_log_prediction_train <- predict(object = poverty_multinolog, newdata = poverty_train_training) 
## table(actual = poverty_train$Target, predict = poverty_log_prediction_train)
## confusionMatrix(poverty_log_prediction_train, poverty_train$Target)

poverty_log_prediction_validation <- predict(object = poverty_multinolog, newdata =poverty_train_validation)
confusionMatrix(poverty_log_prediction_validation, poverty_train_validation$Target)

poverty_log_prediction_test <- predict(object = poverty_multinolog, newdata =poverty_test)

result <-data.frame(poverty_test$Id,poverty_log_prediction_test)
colnames(result) <-c("Id","Target")
write.csv(result,"submission_shuting.csv",row.names = FALSE)

```


[Business recommendations]
Based on our EDA, models and findings anlayses, we have the following recommendations in response to the business questions for the project. <br/>

**1) Recommend variables that are related to schooling, household crowding, house quality, and number of cellphones owned as the most important variables from both the models and EDA analysis. **<br/>

From the models we found that: <br>
More schooling generally indicates that households are less non vunlenerable. <br/>
schooling related variables include:<br/>
Meaneduc，the degree of education 

household crowding related variables: household being crowded generally indicates that households are more impoverished. <br/>
r4t3, Total persons in the household;<br/>
overcrowding  # persons per room 

house quality related variables: worse house quality generally indicates that households are more impoverished <br/>
Cielorazo, the area of the ceilin

number of cellpones owned: more number of cellphones owned generally indicates that households are less non impoverished.<br/>
Qmobilephone

These interpretations from the models are very similar to the ones we got from the boxplots we previously drawn. <br/>

These interpretations may seem to be very intuitive to what we usually think. But this helps us to identify the most important variables to look at when predicting poverty levels. Thus, they do provide some level of practical senses. 



**2) Recommend the random forest model for the Inter-American Development Bank to identify impoverished individuals for the bank to provide the aiding programs. **


[Vision of our project]  <br/>
Our recommendations will help the Inter-American Development Bank identify the impoverished households and improve social inequality by providing sufficient aids to people who are in need of. At the same time, we are making sure that the bank is not wasting their precious aids to non-vulnerable people who do not need the money. Compared to the previous PMT model that the bank is using, our random forest model Although the project is primarily targeted at households in Costa Rica, the models can definitely be applied to other countries and regions in the future, and help the institution to expand its impact in improving inequality issues. 







